With the growth in computing power and sensor capability,
new possibilities are opened for human activity recognition,
for which multiple applications have been proposed.
Most notably, security and health care applications,
such as shoplifting and vandalism detection, fall detection, and respiratory rate sensing.
Some commercial applications are already available,
such as the health and fitness applications found in smart phones and watches,
that automatically detect certain types of exercise.

Typically, wearable sensors are used for human activity recognition.
Using gyroscopes and accelerometers, key positions in the human body can be accurately tracked,
which can be used for very high-performance activity recognition,
given the number of sensors is sufficient.
Wearable sensors have an inherent drawback, though.
They can be cumbersome and unfashionable,
and they require willful equipping.
They also must be battery-powered to enable free movement,
which makes them less reliable than a mains-powered solution.

In the context of human activity recognition,
visible spectrum imaging (RGB camera) has traditionally been the most popular choice for remote sensing.
Unfortunately, the RGB camera is very susceptible to obstructions and varying lightning conditions,
which limits its usefulness.
The RGB camera is also inherently privacy-invasive.
Clearly, there is a demand for other means of remote sensing.
The majority of available data sets for human activity recognition considers only wearable sensors
and visible-spectrum imaging.
To advance the state of human activity recognition via remote sensing,
new data sets are required that consider more remote sensors.

In this thesis, a portable multi-modal data recording system was developed.
The system encompasses an RGB camera, a stereo-vision based depth camera,
a low-resolution infrared camera, a microphone, and a millimeter-wave radar.
This thesis documents the used sensors,
the architecture of the software,
and the data output formats of the software.
The developed system remained slightly unstable,
but still suitable for a small-scale data collection campaign.
The instability was likely due to the used radar device or some programming error.
If the instability can be fixed, the system will be capable of carrying out even larger-scale data collection campaigns.